---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# codebook

<!-- badges: start -->
<!-- badges: end -->

The codebook package is intended to make it easy for users to create codebooks (i.e. data dictionaries) directly from data frame.

## Installation

You can install the development version of codebook like so:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("brad-cannell/codebook")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# library(codebook)
## basic example code
```

# Load data

By default, `codebook` assumes that you want to make a codebook about a dataset file that you have saved somewhere, as opposed to a data frame you're working on in an r session, but don't intend to save. Therefore, the first thing you will need to do is read the data into the current R session.

For the purposes of making a self-contained example, we will actually just create an example data frame in the code chunk below and use it to demonstrate how to use `codebook`

```{r}
set.seed(123)
df <- tibble(
  id = factor(seq(1001, 1020, 1)),
  gender = sample(c("Female", "Male"), 20, TRUE),
  date = sample(seq.Date(as.Date("2015-09-15"), as.Date("2015-10-26"), "day"), 20, TRUE),
  height = rnorm(20, 71, 10)
) %>% 
  print()
```

## Column types

`codebook` classifies all columns as one of four types and uses these categories to determine which descriptive statistics are given in the codebook document:

1. Categorical with many different categories, for example `id` above     
2. Categorical with few different categories, for example `gender` above     
3. Time, for example `date` above    
4. Numeric, for example `height` above    
