---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# codebook

<!-- badges: start -->
<!-- badges: end -->

The codebook package is intended to make it easy for users to create codebooks (i.e. data dictionaries) directly from data frame.

## Installation

You can install the development version of codebook like so:

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("brad-cannell/codebook")
```

## Exported functions

* codebook: The codebook function assists with the creation of a codebook for a given data frame.   

* cb_add_col_attributes: Add arbitrary attributes to columns (e.g., description, source, column type). These attributes can later be accessed to fill in the column attributes table. Note: Column type is the type I say it is: categorical or numeric, Data type is what the computer says it is.

## Simple example

This simple example demonstrates how to use the `codebook` package to make a codebook from a **labeled** data frame. 

```{r example}
library(codebook)
library(dplyr, warn.conflicts = FALSE)
```

### Load data

By default, `codebook` assumes that you want to make a codebook about a dataset file that you have saved somewhere, as opposed to a data frame you're working on in an r session, but don't intend to save. Therefore, the first thing you will need to do is read the data into the current R session.

For the purposes of making a self-contained example, the codebook package comes with a small example data frame that is intended to have some of the features of real study data. We will use it to demonstrate how to use `codebook` below. 

```{r}
# Load example data
data(study)
```

```{r}
glimpse(study)
```

### Column types

`codebook` classifies all columns as one of four types and uses these categories to determine which descriptive statistics are given in the codebook document:

1. Categorical with many different categories, for example the `id` column of the `study` data frame.     
2. Categorical with few different categories, for example the `gender` column of the `study` data frame.     
3. Date, for example the `date` column of the `study` data frame.    
4. Numeric, for example the `height` column of the `study` data frame.    

### Add column attributes

```{r}
# study <- 
study %>% 
  cb_add_col_attributes(
    id,
    description = "Study identification variable"
  ) %>%

  cb_add_col_attributes(
    sex,
    description = "Biological sex of the participant assigned at birth."
  ) %>%
  
  cb_add_col_attributes(
    date,
    description = "Date of enrollment into study."
  ) %>%
  
  cb_add_col_attributes(
    height,
    description = "Participant's height in inches at date of enrollment."
  ) 
```


Get a chunk of code for each column in the data and then copy and paste below.

```{r}
for (i in seq_along(names(study))) {
cat(paste0('
  codebook_add_col_attributes( \n    ',
    names(study)[i], ', \n    ',
    'description = ""
  ) %>%
'))
}
```


















